\section{Question 3}
\subsection{Find Value for x and y}
\paragraph{Consider the linear system of equations
    $$ \begin{pmatrix}
            6 & -4 \\
            8 & -6 \\
            2 & 0
        \end{pmatrix} \begin{pmatrix}
            x \\
            y
        \end{pmatrix} = \begin{pmatrix}
            1 \\
            1 \\
            1
        \end{pmatrix} $$
    Either find a solution or explain why it does not have any solutions.
}
\subsubsection{Analyics}
\paragraph{To determine whether the linear system has a solution, we can check the consistency of the system using the augmented matrix. The augmented matrix for the given system is:
    $
        \begin{matrix}
            \begin{pmatrix}
                6 & -4 & 1 \\
                8 & -6 & 1 \\
                2 & 0  & 1
            \end{pmatrix}
            \overset{Row2 = Row2 - \frac{4}{3} \times Row1}{\longrightarrow} \ \
            \overset{Row3 = Row3 - \frac{1}{3} \times Row1}{\longrightarrow}
            \begin{pmatrix}
                6 & -4           & 1            \\
                0 & -\frac{2}{3} & -\frac{1}{3} \\
                0 & \frac{4}{3}  & \frac{2}{3}
            \end{pmatrix} \\
            \overset{Row2 \times (-3)}{\longrightarrow}
            \begin{pmatrix}
                6 & -4          & 1           \\
                0 & 2           & 1           \\
                0 & \frac{4}{3} & \frac{2}{3}
            \end{pmatrix}   \\
            \overset{Row3 \times (\frac{3}{2})}{\longrightarrow}
            \begin{pmatrix}
                6 & -4 & 1 \\
                0 & 2  & 1 \\
                0 & 2  & 1
            \end{pmatrix}                  \\
            \overset{Row3 = Row3 - Row2}{\longrightarrow}
            \begin{pmatrix}
                6 & -4 & 1 \\
                0 & 2  & 1 \\
                0 & 0  & 0
            \end{pmatrix}
        \end{matrix}
    $}
\paragraph{$\Rightarrow \left\{
        \begin{matrix}
            6x-4y=1 \\
            2y=1
        \end{matrix}
        \Rightarrow
        y=\frac{1}{2},\ x=\frac{1}{2}
        \right.$}
\paragraph{\textbf{Conclusion:} The system has no solution, since there exist two rows of zeros in the augmented matrix. This means that under a given constraint, the values of variables that satisfy all equations can not be found. Mathematically, this usually means that in vector space, the corresponding hyperplane (as defined by the equations) has no point of intersection with it.}
\paragraph{At the same time, this system is underdetermined system. If the number of equations in the system is less than the number of variables, then the system may be underdetermined, there are infinitely many solutions. But if there are contradictions between the equations, then the system may still be unsolvable.}
% 
% 
% 
% 
% 
% 
% 
\subsection{Vector Inclusion in Column Span}
\paragraph{Determine whether or not the vector
    $
        \begin{pmatrix}
            10 \\
            10 \\
            10
        \end{pmatrix}
    $
    in the range (i.e., column span) of the matrix
    $
        \begin{pmatrix}
            1 & 2 \\
            0 & 2 \\
            1 & 3
        \end{pmatrix}
    $.}

% 
% 
% 
% 
% 
\subsubsection{Analytics}
\paragraph{We can perform row reduction or use the concept of matrix multiplication. The augmented matrix for the given system is:
    \[ \left(\begin{array}{cc|c}
            1 & 2 & 10 \\
            0 & 2 & 10 \\
            1 & 3 & 10
        \end{array}\right) \]
}
% 
% 
% 
% 
% 
\paragraph{Performing row operations:}

1. \( R_3 = R_3 - R_1 \)
2. \( R_3 = R_3 - R_2 \)

Results in:

\[ \left[\begin{array}{cc|c} 1 & 2 & 10 \\ 0 & 2 & 10 \\ 0 & 1 & 0 \end{array}\right] \]

Now, further row operations:

3. \( R_1 = R_1 - 2R_2 \)
4. \( R_3 = R_3 - \frac{1}{2}R_2 \)

Result in:

\[ \left[\begin{array}{cc|c} 1 & 0 & -10 \\ 0 & 2 & 10 \\ 0 & 0 & -5 \end{array}\right] \]

The last row indicates that the system is inconsistent (no solution), which means that the vector \( \mathbf{v} = \begin{pmatrix} 10 \\ 10 \\ 10 \end{pmatrix} \) is not in the column span of the matrix \( A \). Therefore, the vector cannot be represented as a linear combination of the columns of matrix \( A \).